Cryptographic assurance of secrecy and fairness in voting

### 2012-12-06 paper/paper.tex
Remove superfluous "organization"
Take a stab at the conclusion

An election involves an information exchange between many independent \term{voters} and a single
\term{election authority} organization.
In a \term{verifiable} election, each voter may verify that her own vote was counted correctly
by the election authority.
A voter, or any other third party \term{auditor}, may also verify the accuracy of the final tallies
reported by the election authority. \cite{preta}
Voting is complicated by the requirement that all votes be secretive to avoid coercion.

@@

>>>>

An election involves an information exchange between many independent \term{voters} and a single
\term{election authority}.
In a \term{verifiable} election, each voter may verify that her own vote was counted correctly
by the election authority.
A voter, or any other third party \term{auditor}, may also verify the accuracy of the final tallies
reported by the election authority. \cite{preta}
Voting is complicated by the requirement that all votes be secretive to avoid coercion.

@@

These systems -- and other similar systems not examined here -- demonstrate how mathematical and
cryptographic techniques can be used to guarantee voters that election results accurately reflect
the votes that were cast by the electorate.

Compared to traditional voting systems, each of the schemes we have examined provides voters a
greater assurance that their votes \emph{are} counted and that the election authority has
\emph{properly} counted all votes that were cast. By satisfying the various facets of ballot
secrecy, they also serve to enforce practices that in general must only be assumed: that voters
cannot be coerced and that a voter is never required to reveal the candidate for whom he/she voted.

However, other potentially-important considerations, such as identity of (non-)voters, are not
addressed by these systems at all but do lay groundwork for further research.
